A survey of HTTP caching implementations on the open Semantic Web

### 2015-02-21 sanity/paper1.tex
Some typo correction
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1041 43ef1190-90fd-4dd7-a769-d0121f02b80e

In spite of this, most of the Semantic Web is unhelpful in even
though it is changing slowly.

@@

Investigate whether curated collections such as LOV or SPARQLES
contain resources that has different characteristics. Since the
different sources we surveyed overlap, this cannot be done with the
simple hypothesis test in this paper, but requires more sophisticated
statistics.

@@

In the next step, we filtered out statements with URIs that were
invalid or irrelevant, e.g. URIs that didn't have a scheme or where
the scheme wasn't HTTP(S), or they were referring to private IP addresses.

>>>>

In spite of this, most of the Semantic Web is unhelpful even though it
is changing slowly.

@@

Investigate whether curated collections such as LOV or SPARQLES
contain resources that have different characteristics. Since the
different sources we surveyed overlap, this cannot be done with the
simple hypothesis test in this paper, but requires more sophisticated
statistics.

@@

In the next step, we filtered out statements with URIs that were
invalid or irrelevant, e.g. URIs that didn't have a scheme or where
the scheme were't HTTP(S), or they were referring to private IP addresses.
